Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-06-26 MUSES_vs_BYOD_solutions.tex
Whops, fixing the first sentence for issue #41, that was incomplete

As these tools have several different access levels and different detection methods. Therefore, we propose the next taxonomy in order to classify the BYOD methods described in this paper.

>>>>

As these tools have several access levels, different detection methods or data control, there exist a number of aspects that the end-user needs to take into account to validate if a product fits his needs. Therefore, we propose the next taxonomy in order to classify the BYOD tools described in this paper.
